
---------- load packages ----------
```{r include=FALSE}
library(tidyverse)
library(nlme)
library(rstatix)
library(ggpubr)
```


---------- load data, split in O2 data and calcification data & exclude outliers after visual inspection of obs-expected percentages ----------
```{r}
#outlier exlusion in conspecific incubations

#O2 meausrements
Data <- read.csv("Data/All_expectedvalues.csv")

Day14 <- Data %>% filter(day =="14")
Day14<- Day14 %>%
  filter(fragment_ID != "AmuD1_AmuB2_AmuA3" & fragment_ID != "SpiA4_SpiB1_SpiD2")

Day5 <- Data %>% filter(day =="5")
Day5<- Day5 %>%
  filter(fragment_ID != "PloB3_PloC3_PloD3")

Data_sub <- Data %>% filter(day != "14" & day != "5")

Data <- rbind(Day14, Day5, Data_sub)

# calcification measurements
# important to delete minus values in expected calc, otherwise relative difference in percentage is wrong
Data_calc <- read.csv("Data/All_expectedvalues.csv")

Day14_calc <- Data_calc %>% filter(day =="14")
Day14_calc<- Day14_calc %>%
  filter(fragment_ID != "AmuD2_AmuB4_AmuA1" & fragment_ID != "AmuD1_AmuB2_AmuA3" & fragment_ID != "AcyB1_AcyD2_AcyA3" & fragment_ID != "PruD4_PruE2_PruA3" & fragment_ID != "PdaA1_PdaB2_PdaD4" & fragment_ID != "AcyB3_AcyD3_AcyA1")

Day5 <- Data %>% filter(day =="5")
Day5_calc<- Day5 %>%
  filter(fragment_ID != "AcyB1_AcyD1_AcyA1")

Day6_calc <- Data_calc %>%  filter(day == "6")
Day6_calc <- Day6_calc %>%  filter(fragment_ID != "PloB3_PcyB4_PruD4")

Data_sub_calc <- Data %>% filter(day != "14" & day != "5"& day != "6")

Data_calc <- rbind(Day6_calc, Day14_calc, Day5_calc, Data_sub_calc)

rm(Data_sub, Data_sub_calc)
```

```{r}
#outlier exclusion in diversity incubations

#O2 measurements
Day13 <- Data %>% filter(day =="13")
Day13<- Day13 %>% filter(fragment_ID != "SpiB2_AcyD2_PcyC3" )

Day9 <- Data %>% filter(day =="9")
Day9<- Day9 %>% filter(fragment_ID != "PdaA2_AmuD2_PruD3" & fragment_ID != "PveF1_MdiC1_PcyB1")

Day7 <- Data %>% filter(day =="7")
Day7<- Day7 %>% filter(fragment_ID != "PdaB4_AcyD3_PcyC4")

Data_sub <- Data %>% filter(day != "13" & day != "9" & day != "7")

Data <- rbind(Day13, Day9, Day7, Data_sub)

# calcification measurements
Day7_calc <- Data_calc %>% filter(day =="7")
Day7_calc<- Day7_calc %>%filter(fragment_ID != "PdaD1_AcyA1_PcyA1")

Day13_calc <- Data_calc %>% filter(day =="13")
Day13_calc<- Day13_calc %>%filter(fragment_ID != "PdaD1_AmuA1_PloD1")

Data_sub_calc <- Data_calc %>%  filter(day != "7" & day != "13")

Data_calc <- rbind(Day7_calc, Day13_calc, Data_sub_calc)
```


---------- calculate difference between observed/measured and expected values and normalize to % ----------
This is percentage error, which is the difference between an experimental and theoretical value, divided by the theoretical value, multiplied by 100 to give a percent.
```{r}
#((100/ exp)* net_obs) -100, rewritten it is ((net_obs/exp)*100)-100, is the same as ((net_obs/exp)-1)*100

Data$exp_obs_net_photo <- with(Data, Data$net_photo_h_surface - Data$exp_Net_photo_ug_h_cm2)
Data$exp_obs_net_photo_perc <- with(Data, ((100 / Data$exp_Net_photo_ug_h_cm2) * Data$net_photo_h_surface)-100)
Data$exp_obs_net_photo_perc <- round(Data$exp_obs_net_photo_perc, 6)

Data$exp_obs_gross_photo <- with(Data, Data$gross_photo_h_surface - Data$exp_Gross_photo_ug_h_cm2)
Data$exp_obs_gross_photo_perc <- with(Data, ((100 / Data$exp_Gross_photo_ug_h_cm2) * Data$gross_photo_h_surface)-100)
Data$exp_obs_gross_photo_perc <- round(Data$exp_obs_gross_photo_perc, 6)

Data$exp_obs_respiration <- with(Data, Data$respiration_h_surface - Data$exp_Resp_ug_h_cm2)
Data$exp_obs_respiration_perc <- with(Data, ((100 / Data$exp_Resp_ug_h_cm2) * Data$respiration_h_surface)-100)
Data$exp_obs_respiration_perc <- round(Data$exp_obs_respiration_perc, 6)

Data_calc$exp_obs_calc <- with(Data_calc, Data_calc$calc_umol_cm2_h - Data_calc$exp_Calc_umol_h_cm2)
Data_calc$exp_obs_calc_perc <- with(Data_calc, ((100 / Data_calc$exp_Calc_umol_h_cm2) * Data_calc$calc_umol_cm2_h)-100)
Data_calc$exp_obs_calc_perc <- round(Data_calc$exp_obs_calc_perc, 6)
```


---------- Splitting dataframe in useful groups ----------
```{r}
min_single_t <- Data %>%  filter(category != "single")
min_single_tc <- Data_calc %>%  filter(category != "single")
biomass_t <- Data %>%  filter(category == "biomass")
conspecific_t <- Data %>%  filter(category == "conspecific")
family_t <- Data %>%  filter(category == "family")
mix_t <- Data %>%  filter(category == "mix")
mix_tc <- Data_calc %>%  filter(category == "mix")
```


#!!!NOTE: Carefull with these graphs as DO start/end values, as well as surface area values and productivity parameters are mathematically coupled. Hence graphs can give an overview, yet can not be interpeted directly.

---------- light incubation start values relationship to change in productivity parameters ----------
```{r}
# monoculture
c1 <-ggplot(min_single_t, aes(x = O2_start_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("All Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

c1a <-ggplot(min_single_t, aes(x = O2_start_L, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("All Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start value"))) +
  ylab(expression(paste("Observed - expected gross photo"))) +
  theme_classic()

c2 <-ggplot(min_single_t, aes(x = O2_end_L, y = exp_obs_respiration)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("All Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end value"))) +
  ylab(expression(paste("Observed - expected resp"))) +
  theme_classic()

c2a <-ggplot(min_single_t, aes(x = O2_end_L, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("All Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end value"))) +
  ylab(expression(paste("Observed - expected gross photo"))) +
  theme_classic()

c2b <-ggplot(min_single_tc, aes(x = TA_umolL_con, y = exp_obs_calc)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("All Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("TA"))) +
  ylab(expression(paste("Observed - expected calc"))) +
  theme_classic()

# diversity incubations
c3 <-ggplot(mix_t, aes(x = O2_start_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

c4 <-ggplot(mix_t, aes(x = O2_end_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  ggtitle("Mixed Incubation") +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

# family incubations
c5 <-ggplot(family_t, aes(x = O2_start_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Family Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

c6 <-ggplot(family_t, aes(x = O2_end_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  geom_point() +
  ggtitle("Family Incubation") +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

# biomass incubations
c7 <-ggplot(biomass_t, aes(x = O2_start_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Biomass Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()


c8 <-ggplot(biomass_t, aes(x = O2_end_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  geom_point() +
  ggtitle("Biomass Incubation") +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

# conspecific incubations
c9 <-ggplot(conspecific_t, aes(x = O2_start_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Conspecific Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

c10 <-ggplot(conspecific_t, aes(x = O2_end_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  geom_point() +
  ggtitle("Conspecific Incubation") +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end value"))) +
  ylab(expression(paste("Observed - expected net photo"))) +
  theme_classic()

# combine all
arranged <- ggarrange(
                     c1,c2,c1a,c2a,c3,c4,c5,c6,c7,c8,c9,c10,c2b,
          label.x = 0,
          label.y = 0.95,
          common.legend = FALSE,
          ncol = 2, nrow =7, 
          hjust = -0.5,
          vjust = 0) +
          theme(legend.text = element_text(size = 40))

ggsave("Graphs/sanity_check.png", width=11, height= 15, limitsize=FALSE, dpi= 700, arranged)
```


---------- light and dark incubation start and end values relationship to productivity parameters ----------
```{r}
# diversity incubations
m1 <-ggplot(mix_t, aes(x = O2_start_L, y = net_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start values light" ))) +
   ylab(expression(paste("Measured net photosynthesis (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m2 <-ggplot(mix_t, aes(x = O2_end_L, y = net_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end values light"))) +
   ylab(expression(paste("Measured net photosynthesis (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m3 <-ggplot(mix_t, aes(x = O2_start_D, y = respiration_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start values dark"))) +
   ylab(expression(paste("Measured respiration (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m4 <-ggplot(mix_t, aes(x = O2_end_D, y = respiration_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end values dark"))) +
   ylab(expression(paste("Measured respiration (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m5 <-ggplot(mix_t, aes(x = O2_start_L, y = gross_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start values light"))) +
   ylab(expression(paste("Measured gross photosynthesis (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m6 <-ggplot(mix_t, aes(x = O2_end_L, y = gross_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 end values light"))) +
   ylab(expression(paste("Measured gross photosynthesis (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m7 <-ggplot(mix_t, aes(x = O2_start_D, y = gross_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("O2 start values dark"))) +
   ylab(expression(paste("Measured gross photosynthesis (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m8 <-ggplot(mix_t, aes(x = O2_end_D, y = gross_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   xlab(expression(paste("O2 end values dark"))) +
   ylab(expression(paste("Measured gross photosynthesis (μg O "[2]," cm" ^-2," h" ^-1,")")))+
   theme_classic()

m9 <-ggplot(mix_tc, aes(x = TA_umolL_con, y = calc_umol_cm2_h)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
  xlab(expression(paste("TA umol/L"))) +
   ylab(expression(paste("Measured calcification (μmol CaCO"[3]," cm" ^-2," h" ^-1,")"))) +
   theme_classic()

arranged <- ggarrange(
                     m1, m2, m3, m4, m5, m6, m7, m8,m9,
          label.x = 0,
          label.y = 0.95,
          common.legend = FALSE,
          ncol = 2, nrow =5, 
          hjust = -0.5,
          vjust = 0) +
          theme(legend.text = element_text(size = 40))

ggsave("Graphs/sanity_check_measured_mix.png", width=11, height= 15, limitsize=FALSE, dpi= 700, arranged)
```


---------- light and dark incubation start and end values relationship to change in  productivity parameters ----------
```{r}
# diversity incubations
e1 <-ggplot(mix_t, aes(x = O2_start_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e2 <-ggplot(mix_t, aes(x = O2_end_L, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e3 <-ggplot(mix_t, aes(x = O2_start_D, y = exp_obs_respiration)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e4 <-ggplot(mix_t, aes(x = O2_end_D, y = exp_obs_respiration)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e5 <-ggplot(mix_t, aes(x = O2_start_L, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e6 <-ggplot(mix_t, aes(x = O2_end_L, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e7 <-ggplot(mix_t, aes(x = O2_start_D, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e8 <-ggplot(mix_t, aes(x = O2_end_D, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

e9 <-ggplot(mix_tc, aes(x = TA_umolL_con, y = exp_obs_calc)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

arranged <- ggarrange(
                     e1, e2, e3, e4, e5, e6, e7, e8,e9,
          label.x = 0,
          label.y = 0.95,
          common.legend = FALSE,
          ncol = 2, nrow =5, 
          hjust = -0.5,
          vjust = 0) +
          theme(legend.text = element_text(size = 40))

ggsave("Graphs/sanity_check_change_mix.png", width=11, height= 15, limitsize=FALSE, dpi= 700, arranged)
```


---------- surface area relationship to productivity parameters ----------
```{r}
# diversity incubations
s1 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = net_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s2 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = respiration_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s3 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = gross_photo_h_surface)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s4 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = calc_umol_cm2_h)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s5 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = net_photo_ug_h)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s6 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = respiration_ug_h)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s7 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = gross_photo_ug_h)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

s8 <-ggplot(mix_tc, aes(x = sum_surface_cm2, y = Calc_umol_h)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

arranged <- ggarrange(
                     s1, s2, s3, s4,s5, s6, s7, s8,
          label.x = 0,
          label.y = 0.95,
          common.legend = FALSE,
          ncol = 2, nrow =4, 
          hjust = -0.5,
          vjust = 0) +
          theme(legend.text = element_text(size = 40))

ggsave("Graphs/sanity_check_surface_meas_mix.png", width=11, height= 15, limitsize=FALSE, dpi= 700, arranged)
```


---------- surface area relationship to change in productivity parameters ----------
```{r}
# diversity incubations
se1 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = exp_obs_net_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

se2 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = exp_obs_respiration)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

se3 <-ggplot(mix_t, aes(x = sum_surface_cm2, y = exp_obs_gross_photo)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()

se4 <-ggplot(mix_tc, aes(x = sum_surface_cm2, y = exp_obs_calc)) +
  geom_smooth(method=lm, color = "black") +
  stat_cor(method = "pearson", p.accuracy = 0.001, r.accuracy = 0.01, size= 6)+
  geom_point() +
  geom_hline(yintercept = 0, linetype = 2, color = "gray86") +
  ggtitle("Mixed Incubation") +
  labs(color = "Productivity score") +
   theme_classic()


arranged <- ggarrange(
                     se1, se2, se3, se4,
          label.x = 0,
          label.y = 0.95,
          common.legend = FALSE,
          ncol = 2, nrow =2, 
          hjust = -0.5,
          vjust = 0) +
          theme(legend.text = element_text(size = 40))

ggsave("Graphs/sanity_check_surface_change_mix.png", width=11, height= 15, limitsize=FALSE, dpi= 700, arranged)
```
